The problem and promise of scale in multilayer networks

### 2019-09-20 paper/unstructured.Rmd
touch on which networks we will focus on

>>>>

## To add

### Introduction?
We determined three types of multilayer networks most relevant to spatial variables
Multilayer networks with layers defined by spatially explicit locations, interspecific interactions, and community or subpopulation structure. 
Other types of networks, such as intercontexual networks or temporal networks, are likely only to incorporate spatial variables in a hybrid multilayer network and considerations for including those variables will be explored here
